\LARGE \bf Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting

### 2014-12-10 main.tex
Rephrase the preliminary new 'Related work' part

A robotic learning agent which employs the learning by teaching paradigm has 
previously been developed by Tanaka and Matsuzoe \cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out 
verbs. The robot is tele-operated and mimics the actions that the children
teach it, but with no long-term memory or learning algorithm in place.
Our work instead focuses on an autonomous robotic partner which the child 
can teach a physical skill.
This differs from the established work of robots learning physical skills
from demonstrations, which has focused exclusively on
the robot learning physical skills for the benefit of the robot -- to play table 
tennis, for example -- not the human teacher \cite{Werfel2014}.

>>>>

Werfel suggests in~\cite{Werfel2014} that, until now, most of the work investigating how
humans can teach robots (in particular, physical skills) focuses on the robot's
benefits, and not so much on the learning experienced by the human tutor. Our
work focuses on this later aspect. A robotic learning agent which employs the learning by teaching paradigm has 
previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
system, children learn vocabulary by teaching the {\sc nao} robot to act out 
verbs. The robot is tele-operated and mimics the actions that the children
teach it, but with no long-term memory or learning algorithm in place.

Our work significantly extends this line of work in two direction, first by
proposing an autonomous robotic partner, second by investigating the scaffolding
of children' acquisition of a challenging physical skill (handwriting).
